---
title: "Fars Analysis"
author: "Bala Yellapantula"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fars Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, collapse = T, comment = "#>")
library(sofars2)
library(dplyr)
library(maps)
library(graphics)
library(tidyr)
```


## SOFARS

This package consists of function which can be used to read, analyze and map FARS( Fatality Analysis Reporting System ) data. FARS is a nationwide census providing NHTSA, Congress and the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.

The following functions are  included in the package:
fars_read()
make_filename()
fars_read_years()
fars_summarize_years()
fars_map_state()
The examples use data from FARS, years 2013-2015, that can be found in the package directory under \extdata folder.

#Read FARS data
This function read data from a file path provided as an argument and returns a tibble with loaded data

```{r}
filename <- system.file("extdata", "accident_2013.csv.bz2", package = "sofars2")
fars_read(filename)
```
#Make a FARS file name
This function creates a filename with the year number which is passed as an argument.

```{r}
make_filename(2013)
```

#Analyze accidents
This function returns a pivot table with number of accidents per year and month. 

```{r}
#system.file("extdata", package = "sofars2")
#system.file("extdata")
#getwd()
setwd("../inst/extdata")
#getwd()
fars_summarize_years(2013)
```

#Plot accident locations
This function takes a state index and year as arguments and returns a map of the state with accident locations plotted.



